Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-12 main_paper.tex
Tweak simulation text a bit more

\section{Simulation Evidence}\label{sim}
This section presents evidence from Monte Carlo simulations that the bootstrap
procedures proposed in Section~\ref{boot} produce valid, robust confidence
intervals (CIs) similar to those obtained by the analytical procedures established in CCT. 
The CIs obtained are comparable to the analytical alternative, and in many cases provide
 coverage closer to the nominal size of the tests in the specifications implemented.
 We also observe that all of the bias corrected methods can offer substantial improvements over estimators that do not bias correct.

The Monte Carlo experiments have a similar structure. For all of them, we generate 500 i.i.d.\ observations from the DGP
\begin{align*}
Y_{i}           &= \mu_{j}(X_{i}) + \varepsilon_{i} \\
X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
\varepsilon_{i} &\sim N(0, 0.1295^2 \times \sigma_i^2) \\
\sigma_i &= z(\gamma) \mu_{j}(X_{i})^\gamma ,
\end{align*}
where $j$ indexes the specific DGP and $z(\gamma)$ is a scale parameter that
ensures that the average variance in a neighborhood around the cutoff
equals the unconditional value under homoskedasticity; i.e. $z(\gamma)$
satisfies
\[
  z(\gamma)^2
    = \frac{1}{\sum_{i = 1}^n \mu_{j}(X_{i})^{2 \gamma}
    \frac{\1\{\min(-\bar h, -\bar b) \leq X_i \leq \max(\bar h,\bar b)\}}
    {\#\{X_i : \min(-\bar h, -\bar b) \leq X_i \leq \max(\bar h, \bar b)\}}};
\]
for $\gamma = 0$ we have $z(\gamma) = 1$ and the errors are
homoskedastic.\footnote{%
  The values $\bar h$ and $\bar b$ are taken as the average values over 500
  homoskedastic simulations of the bandwidths returned by CCT's optimal
  bandwidth selector. This ensures that the relevant variance around the cutoff
  is approximately the same for the heteroskedastic and homoskedastic DGPs.} %
This is the experimental design used by \citet{IK} and CCT for homoskedastic
simulations, which we adopt here to make our simulation results directly
comparable with theirs and with the rest of the literature.  The form of
heteroskedasticity is motivated by \cite{mackinnon2013thirty}. Hence,
 we consider both homoskedastic and heteroskedastic cases by setting $\gamma$ equal to 0 and 2 for the simulations, respectively.
We use the same three functional forms for $\mu_{j}$ as CCT.

@@

To estimate the finite-sample coverage of our new bootstrap based confidence interval, we
simulate 5000 samples from each of the three DGPs ($\gamma = 0$ and $\gamma = 2$) and calculate nominal 95\%
two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
calculate the asymptotic distribution of the bias corrected estimator, and each
of those replications uses an additional 500 replications ($B_1$) to estimate
the bias. The bandwidths, $h$ and $b$,
are chosen using the AMSE-optimal rule proposed by CCT and the wild bootstrap
uses the ``HC3'' transformation of \citet{DF08}.

>>>>

\section{Simulation Evidence}\label{sim}
This section presents evidence from Monte Carlo simulations that the bootstrap
procedures proposed in Section~\ref{boot} produce valid, robust confidence
intervals (CIs) similar to those obtained by the analytical procedures established in CCT. 
 We also observe that all of the bias corrected methods can offer substantial improvements over estimators that do not bias correct.

The Monte Carlo experiments have a similar structure. For all of them, we generate 500 i.i.d.\ observations from the DGP
\begin{align*}
Y_{i}           &= \mu_{j}(X_{i}) + \varepsilon_{i} \\
X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
\varepsilon_{i} &\sim N(0, 0.1295^2 \times \sigma_i^2) \\
\sigma_i &= z(\gamma) \mu_{j}(X_{i})^\gamma ,
\end{align*}
where $j$ indexes the specific DGP and $z(\gamma)$ is a scale parameter that
ensures that the average variance in a neighborhood around the cutoff
equals the unconditional value under homoskedasticity; i.e. $z(\gamma)$
satisfies
\[
  z(\gamma)^2
    = \frac{    {\#\{X_i\ :\ \min(-\bar h, -\bar b) \leq X_i \leq \max(\bar h, \bar b)\}}}
  {\sum_{i = 1}^n \mu_{j}(X_{i})^{2 \gamma}
  \1\{\min(-\bar h, -\bar b) \leq X_i \leq \max(\bar h,\bar b)\}}.
\]
For $\gamma = 0$ we have $z(\gamma) = 1$ and the errors are
homoskedastic.\footnote{%
  The values $\bar h$ and $\bar b$ are taken as the average values over 500
  homoskedastic simulations of the bandwidths returned by CCT's optimal
  bandwidth selector. This ensures that the relevant variance around the cutoff
  is approximately the same for the heteroskedastic and homoskedastic DGPs.} %
This is the experimental design used by \citet{IK} and CCT for homoskedastic
simulations, which we adopt here to make our simulation results directly
comparable with theirs and with the rest of the literature.  The form of
heteroskedasticity is motivated by \cite{mackinnon2013thirty}, and we consider
$\gamma$ equal to 0 and 2 for the simulations.
We use the same three functional forms for $\mu_{j}$ as CCT, which we describe below.

@@

To estimate the finite-sample coverage of our new bootstrap based confidence interval, we
simulate 5000 samples from each of the three DGPs (with $\gamma = 0$ and $\gamma = 2$) and calculate nominal 95\%
two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
calculate the asymptotic distribution of the bias corrected estimator, and each
of those replications uses an additional 500 replications ($B_1$) to estimate
the bias. The bandwidths, $h$ and $b$,
are chosen using the AMSE-optimal rule proposed by CCT and the wild bootstrap
uses the ``HC3'' transformation of \citet{DF08}.
